2H SIP Taxonomy

### 2022-03-25 02_bacdive_taxonomy.Rmd
rename
took out plotting --> dataviz

# Save workspace image

```{r}
# Save a workspace image for figure plotting script
# uncomment to save
# might take a minute
# save.image(file = "cache/qSIP_taxonomy.RData")
```

# Plot Averages

```{r}
fatty_acids_wide_with_tax %>% 
  group_by(phylum) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
  pivot_longer(cols = -phylum, values_to = "Relative Abundance", names_to = "FA") %>% 
  ggplot(aes(x = FA, 
             y = `Relative Abundance`,
             color = phylum,
             fill = phylum)) +
  geom_col() +
  facet_wrap(vars(phylum)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")
```

## Acidobacteria

```{r}
fatty_acids_wide_with_tax %>% 
  group_by(phylum) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
  pivot_longer(cols = -phylum, values_to = "Relative Abundance", names_to = "FA") %>% 
  filter(phylum == "Acidobacteria") %>% 
  ggplot(aes(x = FA, 
             y = `Relative Abundance`,
             color = phylum,
             fill = phylum)) +
  geom_col() +
  facet_wrap(vars(phylum)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")
```

## Proteobacteria

```{r}
FA_w_turnover %>% 
  filter(phylum == "Proteobacteria") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Proteobacteria") +
  theme_bw()
```

## Actinobacteria
```{r}
FA_w_turnover %>% 
  filter(phylum == "Actinobacteria") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Actinobacteria") +
  theme_bw()
```

## Acidobacteria

```{r}
FA_w_turnover %>% 
  filter(phylum == "Acidobacteria") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Acidobacteria") +
  theme_bw()
```

```{r}
FA_w_turnover %>% 
  filter(phylum == "Firmicutes") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Firmicutes") +
  theme_bw()
```

```{r}
FA_w_turnover %>% 
  filter(phylum == "Bacteroidetes") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Bacteroidetes") +
  theme_bw()

@@

```{r}
FA_w_turnover %>% 
  filter(phylum == "Actinobacteria") %>% 
  ggplot(aes(y = rel_area_FID, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Actinobacteria") +
  theme_bw()
```

>>>>

# Export

```{r}
fatty_acids_wide_with_tax %>% saveRDS(file = "cache/bacdive_FA_wide")

fatty_acids_with_tax %>% saveRDS(file = "cache/bacdive_FA")

@@
